The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-21 manuscript/manuscript.Rnw
make ortholog discussion accurate

All 1:1 orthologues present among human, bonobo, mouse, dog, cow,
elephant, and opossum were determined using Ensembl v.64 gene trees
via the Biomart online data management
tool\cite{Kasprzyk2011:BioMartdrivingparadigmchange}. A total of 6882
1:1 orthologous genes were expressed in at least one species. For
further analysis, we eliminated all genes that did not have at least
one species with an $\mathrm{FPKM}\ge10$. A list of these 4259 1:1 orthologous
genes was retained for future analyses of gene expression evolution
described below.

>>>>

All 1:1 orthologues present among \textit{D. novemcinctus}, \textit{P.
  troglodytes}, \textit{B. taurus}, \textit{C. familiaris}, \textit{L.
  africana}, \textit{M. musculus}, \textit{H. sapiens}, and \textit{M.
  domestica} were determined using Ensembl v.80 gene trees via
Biomart\cite{Kasprzyk2011:BioMartdrivingparadigmchange} using the
biomaRt R package \DLA{Cite the biomaRt package}. A total of
\Sexpr{combined.fpkm[species!="homo sapiens" & mean_fpkm >=
  1,length(unique(human_short_name))]} 1:1 orthologous genes were
expressed in at least one species. Of these,
\Sexpr{combined.fpkm[species!="homo sapiens" & mean_fpkm >=
  10,length(unique(human_short_name))]} 1:1 orthologous genes with
\ac{FPKM} $\ge 10$ were retained for future analyses of gene
expression evolution described below.
